A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-02-20 evaluation.tex
Clarify origins of results

We extend the results of SMT-COMP 2023 with our modified \Ostrich{}
on the single-query string solving with linear integer arithmetic constraint
track (QF\_SLIA) in~\cref{tab:solve-status-smt-comp}. We obtain
the results by executing \Ostrich{}~1.3 with CA-Str using
the same benchmarking infrastructure (the StarExec cluster)
and configuration that ran SMT-COMP 2023, combining our new results for CA-Str with the
published results of SMT-COMP 2023. Where avaiable, we use the revised, out-of
competition version of the results for solvers with bugs, including \Ostrich{} and Z3-Noodler.
Note that Z3-Noodler abstained on 70~instances, and thus has a lower total number of results.

>>>>

We extend the results of SMT-COMP 2023 with our modified \Ostrich{}
on the single-query string solving with linear integer arithmetic constraint
track (QF\_SLIA) in~\cref{tab:solve-status-smt-comp}. We obtain
the results by executing \Ostrich{}~1.3 with CA-Str using
the same benchmarking infrastructure (the StarExec cluster)
and configuration that ran SMT-COMP 2023, combining our new results for CA-Str with the
published results of SMT-COMP 2023.
\footnote{StarExec Job ID 59410, "SMT-COMP 2023 single query final", 
\url{https://www.starexec.org/starexec/secure/details/job.jsp?id=59410}.} 
Where avaiable, we use the revised, out-of
competition version of the results for solvers with bugs discovered during
the competition, including \Ostrich{} and Z3-Noodler. 
\footnote{StarExec Job ID 59668, "SMT-COMP 2023 single query final fixed" available at
\url{https://www.starexec.org/starexec/secure/details/job.jsp?id=59668}.}
Note that Z3-Noodler abstained on 70~instances, and thus has a lower total number of results.
We used the parallel results for all solvers.
